Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-04-16 lqg-strings.tex
working on the main file

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they're precisely the same as the ones of regular String Theory. What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
\end{multline}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. From here on, following an analogous procedure to the one found in \cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation} \label{eqn:reality-consequence}
	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
\end{equation}

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p}              & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} \alpha ^{\nu} _{n - p} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-1}         \\
	\widetilde{L} _{n , p} & := \frac{n - p}{E_{n - p}} \alpha ^{\mu} _{p} (\alpha ^{\nu} _{p - n})^{*} \eta _{\mu \nu} = 0 \label{eqn:"Virasoro"-modes-2} .
\end{align}

Before proceeding to quantization, we have one last remark: the 0-th term of the solution reads
\begin{equation} \label{eqn:X-sol-0-term}
	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
\end{equation}
which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) = 0$. Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
\begin{equation} \label{eqn:a-p-relation}
	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation}
Since our Virasoro-like \textquotedblleft modes" are double-indexed without summation, the string rest mass $M^2$ is given only in terms of the 0-th oscillator mode
\begin{equation} \label{eqn:string-rest-mass}
	M^2 = - p^{\mu} p_{\mu} = \frac{1}{16 \pi^2 (\alpha ')^{4}} \alpha ^{\mu} _{0} \alpha ^{\nu} _{0} \eta _{\mu \nu} .
\end{equation}

Collecting our results, we have that the solution for our string is given by
\begin{multline} \label{eqn:KG-Polyakov-solution-final}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
\end{multline}
subject to the infinite family of constraints
\begin{equation}
	L_{n , p} = \widetilde{L}_{n , p} = 0
\end{equation} \label{eqn:"Virasoro"-constraints}
and 0-th oscillation mode related to center of mass momentum
\begin{equation*}
	\alpha ^{\mu} _{0} = 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation*}

@@

In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}. To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
\begin{multline} \label{eqn:canonical-momentum}
	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \big( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \big) \eta _{\nu \mu} ,
\end{multline}
and then we proceed to turn the equal-time Poisson bracket relations
\begin{equation} \label{eqn:Poisson-brackets-1}
	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
\begin{equation} \label{eqn:Poisson-brackets-2}
	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
\end{equation}
into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
\begin{equation} \label{eqn:canonical-commutator-1}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
\begin{equation} \label{eqn:canonical-commutator-2}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
\end{equation}
From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
\begin{equation} \label{eqn:non-vanishing-commutator}
	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
\end{equation}
\begin{equation} \label{eqn:vanishing-commutators}
	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
\end{equation}
which are just harmonic oscillator relations with
\begin{align}
	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
\end{align}
For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
\end{equation}
and for $p = 0$
\begin{equation} \label{eqn:momentum-vacuum}
	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
\end{equation}
Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
\begin{multline} \label{eqn:general-state}
	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
\end{multline}

>>>>

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they're precisely the same as the ones of regular String Theory. What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
\end{multline}
with $E_{p} = \sqrt{p^2 + \mu ^2}$ for the closed string. From here on, we shall deal only with closed strings, unless otherwise stated. Following an analogous procedure to the one found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation} \label{eqn:reality-consequence}
	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
\end{equation}

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p}              & := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu} = 0 , \ \forall \ n , p \in \mathbb{Z} \label{eqn:"Virasoro"-modes-1} \\
	\widetilde{L} _{n , p} & := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{- p})^{*} \eta _{\mu \nu} = 0 , \ n \neq - p \label{eqn:"Virasoro"-modes-2}
\end{align}
\begin{equation} \label{eqn:"Virasoro"-modes-sum}
	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
\end{equation}

Before proceeding, we have one more remark: the 0-th term of the solution reads
\begin{equation} \label{eqn:X-sol-0-term}
	\frac{1}{2 \pi \alpha '} \frac{1}{2 \mu} \left( \alpha ^{\mu} _{0} \e ^{- i \mu \tau} + (\alpha ^{\mu} _{0})^{*} \e ^{i \mu \tau} \right) ,
\end{equation}
which is clearly divergent in the $\mu \rightarrow 0$ limit unless $\mathfrak{Re}(\alpha ^{\mu} _{0}) \sim \mu$. Moreover, if we want to recover the classic String Theory expression in this regime, it is not difficult to see that we require
\begin{equation} \label{eqn:a-p-relation}
	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation}

After analysing closer the $n = - p$ constraint(\ref{eqn:"Virasoro"-modes-sum}), we get the string mass in terms of vibrational modes and center of mass position
\begin{multline} \label{eqn:string-rest-mass}
	M^2 = - p^{\mu} p_{\mu} = \frac{1}{(4 \pi (\alpha ')^2)^2} \Bigg( (2 \pi \alpha ' m)^{2} x^{\mu} x_{\mu} - \\
	- \sum _{n \neq 0} \left( \left( \left( \frac{n}{E_{n}} \right) ^2 - 1 \right) a^{\mu} _{n} (a^{\nu} _{n})^{*} \eta _{\mu \nu} \right) \Bigg) .
\end{multline}

Collecting our results, we have that the solution for our closed string is given by
\begin{multline} \label{eqn:KG-Polyakov-solution-final}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\mu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \Big)
\end{multline}
subject to the family of constraints
\begin{equation} \label{eqn:"Virasoro"-constraints}
	L_{n , p} = \widetilde{L}_{n , p} = 0
\end{equation}
\begin{equation*}
	\sum _{n} \left( \left( \frac{n}{E_{n}} \right) ^2- 1 \right) \widetilde{L}_{n , - n} = 0
\end{equation*}
and 0-th oscillator mode related to center of mass position and momentum
\begin{equation*}
	\alpha ^{\mu} _{0} = 2 \pi \alpha ' \mu x^{\mu} + 4 \pi i (\alpha ')^2 p^{\mu} .
\end{equation*}
One thing to note is that the constraint(\ref{eqn:"Virasoro"-modes-2}) implies we only have $D$ non-zero modes in the solution, since all modes must be mutually orthogonal.

\subsection{The Modes and Constraints Algebra} \label{sec:modes-constraint-algebra}

We start by calculating the momentum canonical to $X^{\mu}$, $\Pi _{\lambda}$:
\begin{multline} \label{eqn:canonical-momentum}
	\Pi _{\lambda} = \frac{\partial \Lagr}{\partial (\partial _{\tau} X^{\lambda})} = \\
	= F^{-} \frac{i}{4 \pi \alpha '} \sum _{n \in \mathbb{Z}} \bigg( - \alpha ^{\nu} _{n} \e ^{i (- E_{n} \tau + n \sigma)} + \\
	+ (\alpha ^{\nu} _{- n})^{*} \e ^{i (E_{n} \tau + n \sigma)} \bigg) \eta _{\nu \lambda}
\end{multline}
and proceed by using the canonical equal-time Poisson bracket between $X^{\mu}$ and $\Pi ^{\nu}$
\begin{equation}
	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}

@@

In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}.

We turn the equal-time Poisson bracket relations into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
\begin{equation} \label{eqn:canonical-commutator-1}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
\begin{equation} \label{eqn:canonical-commutator-2}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
\end{equation}
From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
\begin{equation} \label{eqn:non-vanishing-commutator}
	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
\end{equation}
\begin{equation} \label{eqn:vanishing-commutators}
	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
\end{equation}
which are just harmonic oscillator relations with
\begin{align}
	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
\end{align}
For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
\end{equation}
and for $p = 0$
\begin{equation} \label{eqn:momentum-vacuum}
	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
\end{equation}
Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
\begin{multline} \label{eqn:general-state}
	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
\end{multline}
